Postural developments mediate children's visual access to social information

### 2018-01-24 writeup-cogsci/cogsci2018_faceOnly.Rmd
new 1000 ground truth

ground_truth_data <- read_csv("../data/ground_truth/ground_truth3.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("../data/ground_truth/gold_set_candidates2.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))

>>>>

ground_truth_data <- read_csv("../data/ground_truth/ground_truth4.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("../data/ground_truth/gold_set_candidates2.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))
